\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-03-14 k-planar.tex
Other way of showing planarity

% \todo[inline]{Alternative to the final three paragraphs in the preceding proof:
%
% To see that $H$ is planar, consider the plane multigraph $G''$ obtained by adding a vertex in the interior of each face of $G'$.
% }

>>>>

\todo[inline]{Alternative to the final three paragraphs in the preceding proof:

To see that $H$ is planar, imagine adding a vertex consider a plane multigraph $G''$ obtained by adding a vertex $v_\tau$ in the interior of some of the faces of $G'$.  When creating a new part $S:=V(\tau\cup Q_1\cup Q_2\cup Q_3-F)$ of $\mathcal{P}$, add a vertex $v_\tau$ to the interior of $\tau$ that is adjacent to each vertex of $\tau$.  The graph $G''\supseteq G'$ obtained this way is clearly planar.  Furthermore, for each part $P\in\mathcal{P}$, $G''[P]$ is connected.  Since planarity is preserved under edge contraction, it follows that $G''/\mathcal{P}$ is planar.  Now argue that $G/\mathcal{P}=G''/\mathcal{P}$.
}
